---
title: "Pull stock data from Yahoo! finance"
author: "John Minter"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This shows how to pull financial data from Yahoo! finance and save the data for later analysis.

First, let's start with a clean environment and set up to store the data in our working directory.

```{r}
rm(list=ls())
library(quantmod)
library(xts)
library(rFinFuncs)
```
Now, let's indicate that we want to get new data and our file name.

```{r, warning=FALSE, results='hide'}
bGetNewData <- TRUE
strCsv <- "./VIX.csv"

if(bGetNewData){
  file.remove(strCsv)
  pullSymbolYahoo("^VIX",
                  from = "2008-01-01",
                  savePath = "./",
                  bVerbose = FALSE)
}
```

Note that we removed any old data and pulled down the data.
Data by itself isn't very helpful, so let's first create a
time series.

```{r}
dat.vix <- read.csv(strCsv,header=TRUE)
dat.vix$Date <- as.Date(dat.vix$Date, format="%Y-%m-%d")
dat.vix <- dat.vix[order(dat.vix$Date), ]
dat.vix <- xts(dat.vix[,2:7], order.by=dat.vix[,1])

print(head(dat.vix))
```

We probably want to change the column names to something more meaningful and explore our final object.

```{r}
names(dat.vix) <- c("VIX.Open",
                    "VIX.High",
                    "VIX.Low",
                    "VIX.Close",
                    "VIX.Volume",
                    "VIX.Adj.Close")

print(head(dat.vix))
print(tail(dat.vix))
print(class(dat.vix))
```

Finally, let's plot the data.

```{r, fig.width=7}
plot(dat.vix,
     main="^VIX",
     xlab="Date",
     ylab="Adj Close")
```

